Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-05-05 ch04-lrmhinf/lrmhinf.tex
More conclusion + small stuff everywhere
Add thumb index
(sub)+sections: title case + some \gls{...}

\subsection{Set-up}
Consider an output error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
For an infinitely long data record, this can be described in the time-domain as
\begin{equation}
  y_{\Delta}(n) 
    = 
      y_{\Delta0}(n)
      + v(n) 
    = 
      \Delta(q)u_{\Delta}(n) 
      + H(q)e(n)
  \label{eq:lrmhinf:sysDeltaInfData}
\end{equation}
where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance such that $v(n) = H(q)e(n)$ can be colored noise, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
For a limited data record ($n \in \Set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
\begin{equation}
    y_{\Delta}(n) 
      = 
        \Delta(q)u(n) 
        + H(q)e(n) 
        + t_{\Delta}(n)
    \text{.}
    \label{eq:lrmhinf:sysDeltaFiniteData}
\end{equation}
By applying the \gls{DFT}
\begin{equation}
  X(k) 
       = 
         \frac{1}
              {\sqrt{N}} 
         \sum_{n=0}^{N-1} 
            x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
         \quad   
         \forall k \in \mathbb{Z}
  \label{eq:lrmhinf:DFT}
\end{equation} 
to both sides of~\eqref{eq:lrmhinf:sysDeltaFiniteData}, one obtains:
\begin{equation}
  Y_{\Delta}(k) 
                = 
                  \Delta(\omega_k) U_{\Delta}(k) 
                  + T_{\Delta}(\omega_k) 
                  + V(k) 
  \text{.}
  \label{eq:lrmhinf:sysDeltaFiniteDataFD}
\end{equation}
The $T_{\Delta}$ contribution models the difference between the begin and end conditions of the filters $\Delta$ and $H$ in the measurement~\citep{Pintelon1997ARB}.
The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \Set{\left.\omega_k \right| k = 1,\ldots,N-1}$.

@@

\subsection{A concrete simulation}
Consider a discrete time system $\Delta$ (see \figref{fig:lrmhinf:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
\begin{equation}
  \Delta(z) 
    =  \frac{0.45373 z + 0.44752}
            {z^2 - 1.0595 z + 0.96079}
  \label{eq:lrmhinf:O2sysDT}
  \text{,}
\end{equation}
which has $\timeconst = 50 \unit{samples}$ (i.e. $\damping=0.02$ and $\wn = 1 \unit{rad/s}$).
The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
\begin{equation}
  \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
              {\sqrt{\inv{N}\sum_n v^2(n) }}
       = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
       \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
  \label{eq:lrmhinf:SNR}
\end{equation}
of $10$ is obtained.
%TODO: give the SNR also in frequency domain

@@

\subsection{Study of the experiment length}
The frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.475\columnwidth}
  \photobox{\includegraphics[width=\figurewidth]{\thisDir/figs/avis-airmount-cropped.jpg}}
  \hfill
  \photobox{\includegraphics[width=1.005\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}}
  \caption[\glsentrytext{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
  The left photo shows one of the air mounts providing passive vibration isolation.
  The right photo shows two linear motors that play a role in the active vibration isolation.}
  \label{fig:lrmhinf:avis:details}
\end{figure}

\subsection{Measurement \& control framework}
\label{sec:lrmhinf:control}
The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:lrmhinf:tpc}) with $r_2 = 0$.
The controller $\Controller=\experimental\Controller$ is a diagonal \gls{PI} regulator which stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
See \appref{app:avis-setup} for detailed information regarding both the experimental setup and the experimental controller.
The $r_1$ input consists of five periods of a random phase multisine of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
See \chapref{sec:excitation} and \citep{Geerardyn2013TIM} for more information regarding the design of such a signal.

>>>>

\subsection{Set-Up}
Consider an output error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
For an infinitely long data record, this can be described in the time-domain as
\begin{equation}
  y_{\Delta}(n) 
    = 
      y_{\Delta0}(n)
      + v(n) 
    = 
      \Delta(q)u_{\Delta}(n) 
      + H(q)e(n)
  \label{eq:lrmhinf:sysDeltaInfData}
\end{equation}
where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance such that $v(n) = H(q)e(n)$ can be colored noise, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
For a limited data record ($n \in \Set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
\begin{equation}
    y_{\Delta}(n) 
      = 
        \Delta(q)u(n) 
        + H(q)e(n) 
        + t_{\Delta}(n)
    \text{.}
    \label{eq:lrmhinf:sysDeltaFiniteData}
\end{equation}
By applying the \gls{DFT}
\begin{equation}
  X(k) 
       = 
         \frac{1}
              {\sqrt{N}} 
         \sum_{n=0}^{N-1} 
            x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
         \quad   
         \forall k \in \mathbb{Z}
  \label{eq:lrmhinf:DFT}
\end{equation} 
to both sides of~\eqref{eq:lrmhinf:sysDeltaFiniteData}, one obtains:
\begin{equation}
  Y_{\Delta}(k) 
                = 
                  \Delta(\omega_k) U_{\Delta}(k) 
                  + T_{\Delta}(\omega_k) 
                  + V(k) 
  \text{.}
  \label{eq:lrmhinf:sysDeltaFiniteDataFD}
\end{equation}
The $T_{\Delta}$ contribution models the difference between the begin and end conditions of the filters $\Delta$ and $H$ in the measurement~\citep{Pintelon1997ARB}.
The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \Set{\left.\omega_k \right| k = 1,\ldots,N-1}$.

@@

\subsection{A Concrete Simulation}
Consider a discrete time system $\Delta$ (see \figref{fig:lrmhinf:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
\begin{equation}
  \Delta(z) 
    =  \frac{0.45373 z + 0.44752}
            {z^2 - 1.0595 z + 0.96079}
  \label{eq:lrmhinf:O2sysDT}
  \text{,}
\end{equation}
which has $\timeconst = 50 \unit{samples}$ (i.e. $\damping=0.02$ and $\wn = 1 \unit{rad/s}$).
The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
\begin{equation}
  \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
              {\sqrt{\inv{N}\sum_n v^2(n) }}
       = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
       \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
  \label{eq:lrmhinf:SNR}
\end{equation}
of $10$ is obtained.
%TODO: give the SNR also in frequency domain

@@

\subsection{Study of the Experiment Length}
The frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.475\columnwidth}
  \photobox{\includegraphics[width=\figurewidth]{\thisDir/figs/avis-airmount-cropped.jpg}}
  \hfill
  \photobox{\includegraphics[width=1.005\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}}
  \caption[\glsentryshort{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
  The left photo shows one of the air mounts providing passive vibration isolation.
  The right photo shows two linear motors that play a role in the active vibration isolation.}
  \label{fig:lrmhinf:avis:details}
\end{figure}

\subsection{Measurement \& Control Framework}
\label{sec:lrmhinf:control}
The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:lrmhinf:tpc}) with $r_2 = 0$.
The controller $\Controller=\experimental\Controller$ is a diagonal \gls{PI} regulator which stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
See \appref{app:avis-setup} for detailed information regarding both the experimental setup and the experimental controller.
The $r_1$ input consists of five periods of a random phase multisine of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
See \chapref{sec:excitation} and \citep{Geerardyn2013TIM} for more information regarding the design of such a signal.
